Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-17 writeup/gz_hubble_data.tex

The GZH classifications include 288 unique galaxies originally generated from
SDSS imaging and processed with the \ferengi{} code. The selection spanned a
variety of galaxy morphologies (as selected by GZ2 classifications) and
$r^\prime$-band surface brightnesses, and also spanned the redshift range of
SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target
minimum redshifts in \hst{} imaging.

@@

In addition to the physical parameters of the input images, the \ferengi{}
output depends on assumptions of the global galaxy evolution model. This
evolution is a crude mechanism that mimics the brightness increase of galaxies
with increasing redshift (out to at least $z\sim1-2$). The effect on the
redshifted images is simply an empirical addition to the magnitude of a galaxy
of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
of the effects of ``losing'' spiral/disc features with increasing redshift
for two galaxies with $e=0$.

@@

>>>>

The GZH classifications include 288 unique galaxies originally generated from
SDSS imaging and processed with the \ferengi{} code. The selection spanned a
variety of galaxy morphologies (as selected by GZ2 classifications) and
$r^\prime$-band surface brightnesses, and also spanned the redshift range of
SDSS targets that maximuze the coverage of parameter space.

@@

In addition to the physical parameters of the input images, the \ferengi{}
output depends on assumptions of the global galaxy evolution model. This
evolution is a crude mechanism that mimics the brightness increase of galaxies
with increasing redshift (out to at least $z\sim1-2$). The effect on the
redshifted images is simply an empirical addition to the magnitude of a galaxy
of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
brightens the galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
for values of $e$ starting from $e=0$ and increasing the effect to $e=-3.5$ in
increments of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows
several examples of the effects of ``losing'' spiral/disc features with
increasing redshift for two galaxies with $e=0$.

@@

Another existing study using GZH to select barred galaxies was presented in
\citet{che15}. This study used a slightly different bar selection method to
demonstrate that AGN hosts show no statistically significant enhancement in bar
fraction or average bar likelihood compared to closely-matched inactive
galaxies.
